Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2005-08-12 paper/space.tex
fix references

\[ \hat{h} = \frac{1}{|\mathcal{T}|} \sum_{x \in \mathit{\mathcal{T}}} \mathit{Height}(x) \]
\end{definition}

@@

Consider the tree being built node by node, in any order, as long as the property that it remains a tree during the process is maintained. Each node added, adds a certain amount of weight to the tree. In particular it adds one for each node that sits above it in the tree. This is the same as saying that each node adds its height (which does not change). The weight of the final tree is the sum of all these values.

@@

>>>>

\[ \hat{h} = \frac{1}{|\mathcal{T}|} \sum_{x \in \mathit{\mathcal{T}}} \mathit{Height}(x) \]

\[ h_{max} = \mathit{max}_{x \in \mathcal{T}} \mathit{Height}(x) \]

\end{definition}

@@

\Proof
Consider the tree being built node by node, in any order, as long as the property that it remains a tree during the process is maintained. Each node added, adds a certain amount of weight to the tree. In particular it adds one for each node that sits above it in the tree. This is the same as saying that each node adds its height (which does not change). The weight of the final tree is the sum of all these values.

@@

\begin{lemma}
Given a tree (any tree), we have

\[ h_{max} \leq 2\hat{h} \]
\end{lemma}

\Proof Assume $h_{max} > 2\hat{h}$. Then there is a path, ending in a leaf which lies at depth $h_{max}$. Over this path, there are $h_{max}$ nodes at heights 1, 2, \dots $h_{max}$. The average height over this path is $\frac{1}{h_{max}}\sum_{i=1}^{h_{max}}i=\frac{h_{max}-1}{2}$.
